Replacing standard galaxy profiles with \\ mixtures of Gaussians

### 2013-02-11 documents/mixtures/response_to_referee.txt

fixed.

   Page 6 - Definition of "best": The authors should really have been "bolder" by
   insisting on the use of an information-theoretic measure here rather than the
   "traditional" chi-squared. The MoGs are a natural fit to an image entropy measure
   because maximizing entropy, say, would naturally lead to minimizing the number of
    components in a MoG. Chi-squared is also biased at low signal-to-noise ratios.
   Please consider.

   Page 6: Why is "badness" computed in a one-dimensional numerical integral? For
   the sake of computational speed? What happens when dealing with heavily blended
   objects? Where is the center for the 1D integral then? Please explain. A general
   explanation of how object deblending is performed with MoGs would be welcome.

All we are trying to do in this paper is come up with *replacements*
for the exponential and deVaucouleurs profiles and variants.  We are
not actually fitting real galaxy images.  Indeed that requires
deblending and so on.  Literally, all we are doing is replacing the
exp{r^{1/n}) with a sum of Gaussians.  We are not fitting real scenes.

[ we should make a text change here ]

### 2013-02-11 documents/mixtures/mixture_models.tex
two more referee comments

We seek the \emph{best} MoG approximations.  This necessitates
definition of the word ``best''.  If we think of the profiles as being
two-dimensional probability distribution functions (for, say, the
arrivals of photons), then one natural choice is the K-L divergence or
similar cross-entropy or information-theoretic measure.  However, in
typical astronomical imaging, the galaxy is superimposed on a
substantial, flat sky level, and the noise in the data is close to
Gaussian.  This suggests more chi-squared-like objectives.  We adopt
the latter, in part because they are most appropriate for our specific
proposed application (modeling \sdss-like astronomical imaging), but
experiments we have performed suggest that information-theoretic
objectives also lead to good results.

>>>>

We seek the \emph{best} MoG approximations.  This necessitates
definition of the word ``best''.  If we think of the profiles as being
two-dimensional probability distribution functions (for, say, the
arrivals of photons), then one natural choice is the Kullback-Leibler
divergence or similar cross-entropy or information-theoretic measure.
However, in typical astronomical imaging, the galaxy is superimposed
on a substantial, flat sky level, and the noise in the data is close
to Gaussian.  This suggests more chi-squared-like objectives.  We
adopt the latter, in part because they are most appropriate for our
specific proposed application (modeling \sdss-like astronomical
imaging), but experiments we have performed suggest that
information-theoretic objectives also lead to good results.
